### 2014-04-07 doc/uist14/evaluation.tex
trying to modify evaluation, not clear to me now

In this section, we evaluate our targeting system by benchmarking its performance with an user study. We first describe our design of the physical targeting study, followed by the results in different scenarios.

@@

We break down the time for a complete target acquisition to the following pieces:
$t_{total}=t_{locate}+t_{reorient}+t_{disambiguate}+t_{tap}$
And during the study, we video-taped the participants' behavior and measure each pieces of the time.

@@

\subsection{IR intensity based}

>>>>

\ben{still thinking how to proceed.}
In this section, we evaluate our targeting system by benchmarking its performance with an user study. We first describe our design of the physical targeting study, followed by the results in different scenarios.

@@

We break down the time for a complete target acquisition to the following pieces:
$t_{total}=t_{locate}+t_{reorient}+t_{disambiguate}+t_{tap}$
And during the study, we video-taped the participants' behavior and measure each pieces of the time. The experiment setup is similar to a Fitts' Law target acquisition task. We highlight one of the targets and ask the user to make the selection.

@@

\subsection{IR intensity based}
We evaluate how much gain we can get by performing an automatated disambiguation if the IR intensity reading is available. We compare against the case where no IR intensity is available.
